Stack Safety as a Security Property

### 2020-07-06 main.tex
query in 5
another query in 5

\definition{Eager integrity test}
  Given two machines $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{eager integrity test} if their high-integrity components
  match:
  \[
    \mathit{int}_T ~ \contour ~ \mach ~ \mach' \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\contour) = \mach'(\contour)
    \]

\definition{Eager confidentiality test}
  Given two machine states $\mach_1$ and $\mach_2$ with stepping states and
  observations $\mach_1 \stepstoobs{\obs_1} \mach_1'$ and $\mach_2
  \stepstoobs{\obs_2} \mach_2'$ these satisfy the \emph{eager confidentiality
  test} if their observations and changed components coincide:
  \[
    \mathit{conf}_T ~ \mach_1 ~ \obs_1 ~ \mach_1' ~ \mach_2 ~ \obs_2 ~ \mach_2' ~ \triangleq
    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1' = \mach_2'
  \]

\rb{Fix notations, including for properties below.}
\newcommand{\vse}{\mathit{vse}}
\newcommand{\VSES}{\mathit{VSE}}
\newcommand{\vs}{\mathit{vs}}
\newcommand{\VSS}{\mathit{VS}}

>>>>

\definition{Eager integrity test}
  Given two machines \apt{machine states?} $\mach$ and $\mach'$ and a contour $\contour$, these
  satisfy the \emph{eager integrity test} if their high-integrity components
  match:
  \[
    \mathit{int}_T ~ \contour ~ \mach ~ \mach' \triangleq
    \forall \component . ~
    \contour(\component) = \HIGHINT \rightarrow
    \mach(\contour) = \mach'(\contour)
    \]
\apt{Shouldn't conclusion be $m(k) = m'(k)$ ? }

\definition{Eager confidentiality test}
  Given two machine states $\mach_1$ and $\mach_2$ with stepping states and
  observations $\mach_1 \stepstoobs{\obs_1} \mach_1'$ and $\mach_2
  \stepstoobs{\obs_2} \mach_2'$ these satisfy the \emph{eager confidentiality
  test} if their observations and changed components coincide:
  \[
    \mathit{conf}_T ~ \mach_1 ~ \obs_1 ~ \mach_1' ~ \mach_2 ~ \obs_2 ~ \mach_2' ~ \triangleq
    \obs_1 = \obs_2 \wedge \forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1' = \mach_2'
  \]
\apt{scoping of $\forall$ is ambiguous. Anyhow, shouldn't this be
$
\forall \component . ~
   (     \mach_1(\component) \neq \mach_1'(\component)
    \vee \mach_2(\component) \neq \mach_2'(\component))
    \rightarrow \mach_1'(\component) = \mach_2'(\component)
 $ ?}
\rb{Fix notations, including for properties below.}
\newcommand{\vse}{\mathit{vse}}
\newcommand{\VSES}{\mathit{VSE}}
\newcommand{\vs}{\mathit{vs}}
\newcommand{\VSS}{\mathit{VS}}
